### 2008-12-20 talk/ecoop2009/benchmarks.tex
refactor tables

\anto{these tables are ugly}

\cfbolz{can we make one figure of all the tables?}
\begin{table}[ht]
  \begin{tabular}{|l|r|r|r|r||r|r|}
    \hline
    \textbf{n} & 
    \textbf{Interp} &
    \textbf{JIT} &
    \textbf{JIT 2} &
    \textbf{C\#} &
    \textbf{Interp/JIT 2} &
    \textbf{JIT 2/C\#} \\
    \hline

    $10$    &   0.031  &  0.422  &  0.000  &  0.000  &      N/A  &    N/A \\
    $10^7$  &  30.984  &  0.453  &  0.047  &  0.031  &  661.000  &  1.500 \\
    $10^8$  &     N/A  &  0.859  &  0.453  &  0.359  &      N/A  &  1.261 \\
    $10^9$  &     N/A  &  4.844  &  4.641  &  3.438  &      N/A  &  1.350 \\

    \hline

  \end{tabular}
  \caption{Factorial benchmark}
  \label{tab:factorial}
\end{table}

\begin{table}[ht]
  \begin{tabular}{|l|r|r|r|r||r|r|}
    \hline
    \textbf{n} & 
    \textbf{Interp} &
    \textbf{JIT} &
    \textbf{JIT 2} &
    \textbf{C\#} &
    \textbf{Interp/JIT 2} &
    \textbf{JIT 2/C\#} \\
    \hline

    $10$    &   0.031  &  0.453  &  0.000  &  0.000  &       N/A  &  N/A   \\
    $10^7$  &  29.359  &  0.469  &  0.016  &  0.016  &  1879.962  &  0.999 \\
    $10^8$  &     N/A  &  0.688  &  0.250  &  0.234  &       N/A  &  1.067 \\
    $10^9$  &     N/A  &  2.953  &  2.500  &  2.453  &       N/A  &  1.019 \\

    \hline

  \end{tabular}
  \caption{Fibonacci benchmark}
  \label{tab:fibo}
\end{table}

Tables \ref{tab:factorial} and \ref{tab:fibo} show the seconds spent to calculate
the factorial and Fibonacci for various $n$.  As we can see, for small values
of $n$ the time spent running the JIT compiler is much higher than the time
spent to simply interpret the program.  This is an expected result, as till
now we only focused on optimizing the compiled code, not the compilation
process itself.

@@

\begin{table}[ht]
  \begin{tabular}{|l|r|r|r|r||r|r|}
    \hline
    \textbf{n} & 
    \textbf{Interp} &
    \textbf{JIT} &
    \textbf{JIT 2} &
    \textbf{C\#} &
    \textbf{Interp/JIT 2} &
    \textbf{JIT 2/C\#} \\
    \hline

    $10$    &   0.031  &  0.453  &  0.000  &  0.000  &      N/A  &  N/A   \\
    $10^7$  &  43.063  &  0.516  &  0.047  &  0.063  &  918.765  &  0.750 \\
    $10^8$  &     N/A  &  0.875  &  0.453  &  0.563  &      N/A  &  0.806 \\
    $10^9$  &     N/A  &  4.188  &  3.672  &  5.953  &      N/A  &  0.617 \\

    \hline

  \end{tabular}
  \caption{Accumulator benchmark}
  \label{tab:accumulator}
\end{table}

Table \ref{tab:accumulator} show the results for the benchmark.  Again, we can
see that the speedup of the JIT over the interpreter is comparable to the
other two benchmarks.  However, the really interesting part is the comparison
with the equivalent C\# code, as the code generated by the JIT is
\textbf{faster}.

>>>>

\begin{table}[ht]
  \begin{center}

  \begin{tabular}{l|rrrrrr}
    \multicolumn{5}{c}{\textbf{Factorial}} \\ [0.5ex]

    \textbf{$n$}          & $10$  & $10^7$           & $10^8$         & $10^9$         \\
    \hline
    \textbf{Interp}       & 0.031 & 30.984           & N/A            & N/A            \\
    \textbf{JIT}          & 0.422 &  0.453           & 0.859          & 4.844          \\
    \textbf{JIT 2}        & 0.000 &  0.047           & 0.453          & 4.641          \\
    \textbf{C\#}          & 0.000 &  0.031           & 0.359          & 3.438          \\
    \textbf{Interp/JIT 2} & N/A   & \textbf{661.000} & N/A            & N/A            \\
    \textbf{JIT 2/C\#}    & N/A   & \textbf{1.500}   & \textbf{1.261} & \textbf{1.350} \\ [3ex]

    \multicolumn{5}{c}{\textbf{Fibonacci}} \\ [0.5ex]

    \textbf{$n$}          & $10$  & $10^7$           & $10^8$         & $10^9$         \\
    \hline
    \textbf{Interp}       & 0.031 & 29.359           & 0.000          & 0.000          \\
    \textbf{JIT}          & 0.453 &  0.469           & 0.688          & 2.953          \\
    \textbf{JIT 2}        & 0.000 &  0.016           & 0.250          & 2.500          \\ 
    \textbf{C\#}          & 0.000 &  0.016           & 0.234          & 2.453          \\
    \textbf{Interp/JIT 2} & N/A   & \textbf{1879.962}& N/A            & N/A            \\
    \textbf{JIT 2/C\#}    & N/A   & \textbf{0.999}   & \textbf{1.067} & \textbf{1.019} \\
  \end{tabular}

  \end{center}
  \caption{Factorial and Fibonacci benchmarks}
  \label{tab:factorial-fibo}
\end{table}

Table \ref{tab:factorial-fibo} shows the seconds spent to calculate
the factorial and Fibonacci for various $n$.  As we can see, for small values
of $n$ the time spent running the JIT compiler is much higher than the time
spent to simply interpret the program.  This is an expected result, as till
now we only focused on optimizing the compiled code, not the compilation
process itself.

@@

\begin{table}[ht]
  \begin{center}

  \begin{tabular}{l|rrrrrr}
    \multicolumn{5}{c}{\textbf{Accumulator}} \\ [0.5ex]

    \textbf{$n$}          & $10$  & $10^7$           & $10^8$         & $10^9$         \\
    \hline
    \textbf{Interp}       & 0.031 & 43.063           & N/A            & N/A            \\
    \textbf{JIT}          & 0.453 &  0.516           & 0.875          & 4.188          \\
    \textbf{JIT 2}        & 0.000 &  0.047           & 0.453          & 3.672          \\
    \textbf{C\#}          & 0.000 &  0.063           & 0.563          & 5.953          \\
    \textbf{Interp/JIT 2} & N/A   & \textbf{918.765} & N/A            & N/A            \\
    \textbf{JIT 2/C\#}    & N/A   & \textbf{0.750}   & \textbf{0.806} & \textbf{0.617} \\

  \end{tabular}
  \end{center}
  \caption{Accumulator benchmark}
  \label{tab:accumulator}
\end{table}

Table \ref{tab:accumulator} show the results for the benchmark.  Again, we can
see that the speedup of the JIT over the interpreter is comparable to the
other two benchmarks.  However, the really interesting part is the comparison
with the equivalent C\# code, as the code generated by the JIT is up to 1.62 times
\textbf{faster}.
